Carbonate chemistry at Ny-Ålesund

### 2021-12-26 awipev-CO2.Rmd
changed output in yaml

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  pdf_document: default
  word_document: default
  html_document: default
  odt_document: default
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

>>>>

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output: html_document
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---
